Process Genotypes For Ancestry Analysis

### 2019-09-19 code/Ancestry_PCA.Rmd
Ancestry Chunk1v2

    gunzip ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
    rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf
done

@@

rm 1000Genomes_chr*
rm *.list
```

###Takeout INDV for PCA Population
cat CEU.samples.list YRI.samples.list CHB.samples.list JPT.samples.list > 1000G_IDV.list
paste 1000G_IDV.list 1000G_IDV.list > foo.txt;
mv foo.txt 1000G_IDV.list

rm *.samples.list;

plink --threads $CORES --bfile 1000Genomes --snps-only --keep 1000G_IDV.list --make-bed --out INDV_1000G_Pops
rm 1000Genomes.*
```

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
CORES=$(nproc)
##Pull VCF Files from Synapse
synapse get -r syn11707204 --downloadLocation VCF/

@@

  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --out GWAS_Plink/MSSB_Chr_$i

>>>>

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done

@@

rm 1000Genomes_chr*
rm *.list
rm *.panel

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
CORES=$(nproc)
##Pull VCF Files from Synapse
mkdir VCF
synapse get -r syn11707204 --downloadLocation VCF/

@@

  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
